Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-23 manuscript/draft.Rmd
fig 5 clarify

![Performance of all six models over time, according to three metrics. **A.**
Root mean square error (rmse) describes the distance between each model's point
estimates and the observed richness values. Note that the three environmental
models tend to show the largest errors. **B.** Deviance (-2 times the Gaussian
log-likelihood) describes the lack of fit of entire predictive distributions.
Note that the stack of single-species random forest SDMs shows much higher error
than the other models (since its predictions are too confident), and that the
"naive" model's deviance grows relatively quickly (as its predictions become
broader and less informative). **C.** Coverage of a model's 95% confidence
intervals indicates how often the observed values fall inside the predicted
range. For well-calibrated models, the coverage of the 95% confidence intervals
should be 95%. As in the previous panel, the "naive" model's predictive
distribution is too wide (capturing almost all of the data) and the stacked
SDM's predictive distribution is too narrow (missing almost a third of the
observed richness values by 2014).](../figures/performance_time.png)

>>>>

![Performance of all six models over time, according to three metrics. **A.**
Root mean square error (rmse) describes the distance between each model's point
estimates and the observed richness values. Note that the three environmental
models tend to show the largest errors. **B.** Deviance (-2 times the Gaussian
log-likelihood) describes the lack of fit of entire predictive distributions.
Note that the stack of single-species random forest SDMs shows much higher error
than the other models (since its predictions are too confident, see Fig. 1), and 
that the "naive" model's deviance grows relatively quickly (as its predictions
become broader and less informative, see Fig. 1). **C.** Coverage of a model's
95% confidence intervals indicates how often the observed values fall inside the
predicted range. For well-calibrated models, the coverage of the 95% confidence
intervals should be 95% (indicated by the black line). As in the previous panel,
the "naive" model's predictive distribution is too wide (capturing almost all of
the data) and the stacked SDM's predictive distribution is too narrow (missing
almost a third of the observed richness values by 2014).](../figures/performance_time.png)
